### 2022-05-27 chapters/04-chapter-4.tex
txs auto checkin

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
	\begin{tabular}{@{}llccl@{}}
		\toprule
		\rowcolor[HTML]{009901} 
		\multicolumn{1}{c}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{ID}}} &
		\multicolumn{1}{c}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{Service (Fungsi)}}} &
		\multicolumn{1}{l}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{Extra Latency}}} &
		\multicolumn{1}{l}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{User}}} &
		{\color[HTML]{FFFFFF} \textbf{Keterangan}} \\ \midrule
		\multicolumn{1}{|l|}{I1} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{100ms} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus extra latency \#1} \\ \midrule
		\multicolumn{1}{|l|}{I2} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{250ms} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus extra latency \#2} \\ \midrule
		\multicolumn{1}{|l|}{I3} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{350ms} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus extra latency \#3} \\ \midrule
		\multicolumn{1}{|l|}{I4} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{250ms} &
		\multicolumn{1}{c|}{75} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular}} \\ \midrule
		\multicolumn{1}{|l|}{I5} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{250ms} &
		\multicolumn{1}{c|}{150} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular}} \\ \midrule
		\multicolumn{1}{|l|}{I6} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{-} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus peningkatan kerja CPU} \\ \midrule
		\multicolumn{1}{|l|}{} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{l|}{} \\ \cmidrule(lr){2-2}
		\multicolumn{1}{|l|}{} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}ProductCatalog (getproduct\\ listproducts)\end{tabular}} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{l|}{} \\ \cmidrule(lr){2-2}
		\multicolumn{1}{|l|}{} &
		\multicolumn{1}{l|}{ShippingService (getquote)} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{l|}{} \\ \cmidrule(lr){2-2}
		\multicolumn{1}{|l|}{\multirow{-4}{*}{I7}} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}RecommendationService \\ (listrecommendations)\end{tabular}} &
		\multicolumn{1}{c|}{\multirow{-4}{*}{250ms}} &
		\multicolumn{1}{c|}{\multirow{-4}{*}{25}} &
		\multicolumn{1}{l|}{\multirow{-4}{*}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency\\  dengan beberapa service\end{tabular}}} \\ \bottomrule
	\end{tabular}
\end{table}

>>>>

\begin{flushleft}
	% Please add the following required packages to your document preamble:
	% \usepackage{multirow}
	% \usepackage[table,xcdraw]{xcolor}
	% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
	\begin{table}[]
		\begin{tabular}{llccl}
			\hline
			\rowcolor[HTML]{009901} 
			\multicolumn{1}{c}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{ID}}} &
			\multicolumn{1}{c}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{Service (Fungsi)}}} &
			\multicolumn{1}{l}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{Extra Latency}}} &
			\multicolumn{1}{l}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{User}}} &
			{\color[HTML]{FFFFFF} \textbf{Keterangan}} \\ \hline
			\multicolumn{1}{|l|}{I1} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{100ms} &
			\multicolumn{1}{c|}{25} &
			\multicolumn{1}{l|}{Kasus extra latency \#1} \\ \hline
			\multicolumn{1}{|l|}{I2} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{250ms} &
			\multicolumn{1}{c|}{25} &
			\multicolumn{1}{l|}{Kasus extra latency \#2} \\ \hline
			\multicolumn{1}{|l|}{I3} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{350ms} &
			\multicolumn{1}{c|}{25} &
			\multicolumn{1}{l|}{Kasus extra latency \#3} \\ \hline
			\multicolumn{1}{|l|}{I4} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{250ms} &
			\multicolumn{1}{c|}{75} &
			\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular}} \\ \hline
			\multicolumn{1}{|l|}{I5} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{250ms} &
			\multicolumn{1}{c|}{150} &
			\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular}} \\ \hline
			\multicolumn{1}{|l|}{I6} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{-} &
			\multicolumn{1}{c|}{25} &
			\multicolumn{1}{l|}{Kasus peningkatan kerja CPU} \\ \hline
			\multicolumn{1}{|l|}{} &
			\multicolumn{1}{l|}{CheckoutService (placeorder)} &
			\multicolumn{1}{c|}{} &
			\multicolumn{1}{c|}{} &
			\multicolumn{1}{l|}{} \\ \cline{2-2}
			\multicolumn{1}{|l|}{} &
			\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}ProductCatalog (getproduct\\ listproducts)\end{tabular}} &
			\multicolumn{1}{c|}{} &
			\multicolumn{1}{c|}{} &
			\multicolumn{1}{l|}{} \\ \cline{2-2}
			\multicolumn{1}{|l|}{} &
			\multicolumn{1}{l|}{ShippingService (getquote)} &
			\multicolumn{1}{c|}{} &
			\multicolumn{1}{c|}{} &
			\multicolumn{1}{l|}{} \\ \cline{2-2}
			\multicolumn{1}{|l|}{\multirow{-4}{*}{I7}} &
			\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}RecommendationService \\ (listrecommendations)\end{tabular}} &
			\multicolumn{1}{c|}{\multirow{-4}{*}{250ms}} &
			\multicolumn{1}{c|}{\multirow{-4}{*}{25}} &
			\multicolumn{1}{l|}{\multirow{-4}{*}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency\\  dengan beberapa service\end{tabular}}} \\ \hline
		\end{tabular}
	\end{table}
\end{flushleft}
